### 2016-02-01 p00-ch00-intro/intro.tex
Add Pony lang in the by-design category

In this section, we briefly provide an overview of the programming languages that have targetted similar problem statements.
It is important to note the rapid evolution of programming languages trying to provide an actor-based model of asynchronous message passing.\TODO{Reference}
In addition, we identify different types of research and work related to actor model and concurrency programming:
\begin{description}
\item[First-Class Citizen]
%is the type of programming languages that deliver actor model programming support as a first-class citizen of the language.
Languages in which the actor model is by-design part of the syntax and semantics of the language.
\TODO{Cite polylang as a research recent lang.}
\TODO{Why this category is the best}
\item[Implicit By Design]
refers to the type that there is no explicit notion of actor models in the language syntax or semantics.
However, the programming language provides fundamental constructs for concurrency and asynchronous message passing.
Thus, it becomes an easy task in this kind of programming language to create an abstraction to support the actor model by coding.
\item[External Library]
refers to the type of programming languages for which actor model support is provided by an external library developed for the language.
\end{description}

>>>>

In this section, we briefly provide an overview of the programming languages that have targetted similar problem statements.
It is important to note the rapid evolution of programming languages trying to provide an actor-based model of asynchronous message passing.\TODO{Reference}
In addition, we identify different types of research and work related to actor model and concurrency programming:
\begin{description}
\item[First-Class Citizen]
%is the type of programming languages that deliver actor model programming support as a first-class citizen of the language.
Languages in which the actor model is by-design part of the syntax and 
semantics of the language.
Pony~\cite{ponylang,ClebschD13} targets high-performance 
computing using actor models and shared memory. 
When actor model is part of the design of a language, formal verification
and correctness of actor semantics at runtime yields naturally from the 
language semantics at runtime.
\item[Implicit By Design]
refers to the type that there is no explicit notion of actor models in the language syntax or semantics.
However, the programming language provides fundamental constructs for concurrency and asynchronous message passing.
Thus, it becomes an easy task in this kind of programming language to create an abstraction to support the actor model by coding.
\item[External Library]
refers to the type of programming languages for which actor model support is provided by an external library developed for the language.
\end{description}
